Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-31 article/02_Materials_and_Methods.Rmd
also the table headers

```{r dactb, echo=FALSE, tidy=FALSE}
load("distance_and_correlation_table_B.RData")
distance_and_correlation_table_B %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Correlation")),
    list(~kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black")))
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    list(~kableExtra::cell_spec(., "latex", bold = . < 0.1))
  ) %>%
knitr::kable(
  "latex",
  caption = "Like Table \\ref{tab:dacta}. \\textbf{C} shows the Mantel test results for the distance networks based on the two variables if compared directly, \\textbf{D} the results of the respective Partial Mantel test considering and correcting for spatial distance as a second independent variable.",
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "type & construction distance" = 2, "type & construction & spatial distance" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "C" = 2, "D" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(1), width = "4cm") %>%
  gsub("table", "table*", .)
```

>>>>

```{r dactb, echo=FALSE, tidy=FALSE}
load("distance_and_correlation_table_B.RData")
distance_and_correlation_table_B %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Correlation")),
    list(~kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black")))
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    list(~kableExtra::cell_spec(., "latex", bold = . < 0.1))
  ) %>%
knitr::kable(
  "latex",
  caption = "Like Table \\ref{tab:dacta}. \\textbf{C} shows the Mantel test results for the distance networks based on the two variables if compared directly, \\textbf{D} the results of the respective Partial Mantel test considering and correcting for spatial distance as a second independent variable.",
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "type & construction distance" = 2, "type & construction + spatial distance" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "C" = 2, "D" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(1), width = "4cm") %>%
  gsub("table", "table*", .)
```
